---
title: "Untitled"
format: 
  docx:
    reference-doc: modeloTest.dotx
editor: visual
execute: 
  echo: false
  warning: false
lang: pt
---

## Quarto

::: {custom-style="Citação - ABNT"}
This is formatted according to the Citação - ABNT dkaskdsahkdhsadsadasdsadsadasdsadsadsadsadsadsaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa.
:::

```{r}
#| label: start


library(tidyverse)
library(quantmod)
library(scales)
library(PerformanceAnalytics)
library(openxlsx)
library(corrplot)
library(RColorBrewer)
library(knitr)

symbols = c("BTC-USD","ETH-USD","USDC-USD","USDT-USD","BNB-USD","XRP-USD","ADA-USD","DOGE-USD","SOL-USD","MATIC-USD")

asset_return = readRDS("outputData/assetReturn8.rds")
correlation = cor(asset_return)
```

## test

```{r}
#| label: tbl-demonstração
#| tbl-cap: Demonstração
#| class-output: tabela - abnt

x = correlation %>% as.data.frame() %>% rownames_to_column("ATIVO")

tbl = kable(x,
      format = "simple",
      digits = 3,
      format.args = list(scientific=FALSE,big.mark = ".",decimal.mark=",",justify="left"))

tbl

```



veja em @tbl-demonstração

{{< pagebreak >}}

## outrotest

```{mermaid}
flowchart LR
  A[dados] --> B[obtenção]
  B --> E[quantmod]
  B --> F[tidyverse]
  A --> C[manipulação]
  C --> F
  C --> G[PerformanceAnalytics]
  C --> H[base]
  A --> D[Gráfico e tabela]
  D --> F
  D --> I[scales]
  D --> J[corrplot]
  D --> K[RColorBrewer]
  D --> L[knitr]
  
```

{{< pagebreak >}}

```{dot}
graph G {
  layout=neato
   tidyverse -- GRAFICO;
   scales -- GRAFICO;
   corrplot -- GRAFICO;
  RColorBrewer -- GRAFICO; 
  tidyverse -- DADOS;
  quantmod -- DADOS;
  PerformanceAnalytics -- DADOS;
  base -- DADOS;
  tidyverse -- TABELA;
  knitr -- TABELA;
  
}
```
